Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-11 paper/main.tex
minor changes to discussion of robustness

\todo[inline]{following is one exemplary sentence that would benefit from also
mentioning that clusters should not be all over the brain which could be the
case because naturalistic paradigm / confounding variables etc.}

% study goal
The goal of this study was to investigate if cues about the spatial layout
embedded in two naturalistic stimuli correlate with increased hemodynamic
activity in the PPA that was define by using a visual localizer experiment
within the same subjects \citep{sengupta2016extension}.
% what we did We
annotated a \unit[2]{h} movie and its temporally aligned audio-description to
create GLM contrasts similar to previous studies that used conceptualized
stimuli.
% group level
On a group average level, we compare results gained from both naturalistic
stimuli to results gained from the visual localizer.
% individual level
On the level single subjects, we also assess localization performance of a
``visual area'' using the auditory stimulus.\todo{``localization'' performance}
% NeuroVault
Unthreholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts for both naturalistic stimuli can be found
at \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
private collection}

@@

% why we did a couple of contrasts
For both stimuli we created several contrasts that varied the amount of
events available for the analysis and how well the annotated events within
categories on average matched the stimulus type that we assumed to be
preferentially processed in the PPA.
% PPA AO
Regarding contrasts of the AO stimulus, six of eight contrasts show significant
bilateral clusters in the anterior part of the group PPA overlap.
% PPA AV
Regarding contrasts of the AV stimulus, all five contrasts show significant
bilateral clusters in the PPA but extending into more posterior brain regions.
% results indicate robustness
Thus, the results of the additional contrasts indicate that our findings are
robust across contrasts and do not depend on the design of one specific
contrasts.

% but
Nevertheless, results also suggest that ``localization performance'' depends on
the amount of available data and how well the feature space is modeled.
% example
For example, contrast 8 of the AO stimulus (\texttt{se\_new} > texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA.
% concluding statement
Hence, investigators using model-driven analyses have to consider how many
events a stimulus to be chosen may provide and how homogeneous the events to be
averaged might be.

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find many [random] clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo{ouff\dots}
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention, eye movements[, or
memory].\todo{which kind of memory}
% AO: auditory cortices
Nevertheless, contrasts of the AO stimulus that compare verbal cues about the
change of a setting (\texttt{se\_new} or \texttt{se\_old}) to categories that do
not cue a change of a setting (contrasts 2, 3, 6, 7) show significant clusters
in (primary and secondary) auditory cortices.\todo{``poor job of nuisance
regressors?}
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across trials and nuisance regressors did not capture enough
variance.\todo{ouf\dots}
% possible reason
This could be attributed to a possible change of the soundscape when the
narrative switches to a new setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should (extensively) annotate the stimulus material
and test for correlations among variables.

@@

todo[inline]{in 11 subjects there are voxels of higher z-score (in the PPA ROI)
    in the AO contrast than in the contrast of the visual localizer -> should
    all be in the anterior part of the PPA ROI, i.e. the area that belongs to
    the significant cluster of the AO contrast}

>>>>

% study goal
The goal of this study was to investigate if cues about the spatial layout
embedded in two naturalistic stimuli correlate with increased hemodynamic
activity in the PPA that was define by using a visual localizer experiment
within the same subjects \citep{sengupta2016extension}.
% what we did We
We annotated a \unit[2]{h} movie and its temporally aligned audio-description to
create GLM contrasts similar to previous studies that used conceptualized
stimuli.
% group level
On a group average level, we compare results gained from both naturalistic
stimuli to results gained from the visual localizer.
% individual level
On the level single subjects, we also assess localization performance of a
``visual area'' using the auditory stimulus.\todo{``localization'' performance}
% NeuroVault
Unthreholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts for both naturalistic stimuli can be found
at \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.\todo{still
private collection}

@@

% why we did a couple of contrasts
For both stimuli we created several contrasts that varied the amount of events
available for the analysis and how well the annotated events within categories
on average matched the stimulus type that we assumed to be preferentially
processed in the PPA.
% PPA AO
Regarding contrasts of the AO stimulus, six of eight contrasts show significant
bilateral clusters in the anterior part of the group PPA overlap.
% PPA AV
Regarding contrasts of the AV stimulus, all five contrasts show significant
bilateral clusters in the PPA but also extending into more posterior brain
regions.
% results indicate robustness
Thus, the results of the additional contrasts indicate that our findings are
robust across contrasts do not depend on the design of one specific
contrasts.

% but
Nevertheless, results are still influcended by [sensitive to] the amount of
available data and how well the feature space is modeled.
% example
For example, contrast 8 of the AO stimulus (\texttt{se\_new} > texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA.
% concluding statement
Hence, investigators using model-driven analyses have to consider how many
events a stimulus to be chosen may provide and how homogeneous the events to be
averaged might be.

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find many [random] clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo{ouff\dots}
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention or eye movements\todo{should
already be mentioned in disc. of primary contrasts}
% AO: auditory cortices
Nevertheless, contrasts of the AO stimulus that compare verbal cues about the
change of a setting (\texttt{se\_new} or \texttt{se\_old}) to all non-spatial
categories (cf. contrasts 2, 3, 6, 7) show significant clusters in (primary and
secondary) auditory cortices.
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across trials and nuisance regressors did not capture enough
variance.\todo{ouf\dots}
% possible reason
Significant clusters in auditory cortices could be correlating with a possible
change of the soundscape when the narrator of the audio-description (or a cut in
the movie) switches to a another setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should (extensively) annotate the stimulus material
and test for correlations among variables.

@@

\todo[inline]{in 11 subjects there are voxels of higher z-score (in the PPA ROI)
    in the AO contrast than in the contrast of the visual localizer -> should
    all be in the anterior part of the PPA ROI, i.e. the area that belongs to
    the significant cluster of the AO contrast}
